Flute and kink instabilities in a dynamically twisted flux tube with anisotropic plasma viscosity

### 2022-02-15 paper.tex
Do todos

\begin{figure*}
  \centering
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{kinetic_energy-4.pdf}
      \caption{Kinetic Energy}
      \label{fig:kink_ke-4}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{kinetic_energy_log-4.pdf}
      \caption{Growth rate estimation}
      \label{fig:kink_ke_log-4}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{heating_r-4.pdf}
      \caption{Viscous and Ohmic heating}
      \label{fig:heating-4}
    \end{subfigure}
  \mycaption{Kinetic energy \rev{and heating} as a function of time showing the development and
  measured growth rates $\gamma$ and $\lambda$ of the flute and kink
  instabilities, respectively.}{Resistivity is $\eta=10^{-4}$ and Figure~\ref{fig:kink_ke_log-4} is a enlarged version of the first. \rev{The viscous heating associated with the flute instability (that generated before $t\approx28$) is negligible compared to that associated with the kink instability. While the isotropic model permits greater viscous heating (on the order of two orders of magnitude), the anisotropic model enhances Ohmic heating.}}
\label{fig:kink_str8_ke-4}%
\end{figure*}

@@

\todo{change u_r to u_x in kink perturbation plot}

@@

\begin{figure*}
  \centering
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{kinetic_energy-3.pdf}
      \caption{Kinetic Energy}
      \label{fig:kink_ke-3}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{kinetic_energy_log-3.pdf}
      \caption{Growth rate estimation}
      \label{fig:kink_ke_log-3}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{heating_r-3.pdf}
      \caption{Cumulative heat}
      \label{fig:heating_r-3}
    \end{subfigure}
\mycaption{Kinetic energy \rev{and heating} as a function of time in the cases where
$\eta=10^{-3}$.}{The results from both viscosity models are shown. The flute
instability appears earlier than where $\eta=10^{-4}$ and the growth rate of
the kink instability is decreased. \rev{While the heat generated via viscous heating is orders of magnitude lower when using anisotropic viscosity, Ohmic heating is enhanced by the use of the anisotropic model.}}
\label{fig:kink_str8_ke-3}%
\end{figure*}

\todo{put Q_... in angle brackets and explain what it means in caption}

>>>>

\begin{figure*}
  \centering
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{kinetic_energy-4.pdf}
      \caption{Kinetic Energy}
      \label{fig:kink_ke-4}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{kinetic_energy_log-4.pdf}
      \caption{Growth rate estimation}
      \label{fig:kink_ke_log-4}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{heating_r-4.pdf}
      \caption{Cumulative heating}
      \label{fig:heating-4}
    \end{subfigure}
  \mycaption{Kinetic energy \rev{and heating} as a function of time showing the development and
  measured growth rates $\gamma$ and $\lambda$ of the flute and kink
  instabilities, respectively.}{Resistivity is $\eta=10^{-4}$ and Figure~\ref{fig:kink_ke_log-4} is a enlarged version of the first. \rev{The cumulative heating $\langle Q_{*} \rangle$ where $*$ is either $\nu$ for viscous heating or $\eta$ for Ohmic heating is the total heat integrated over both time and space up to a time $t$. The viscous heating associated with the flute instability (that generated before $t\approx28$) is negligible compared to that associated with the kink instability. While the isotropic model permits greater viscous heating (on the order of two orders of magnitude), the anisotropic model enhances Ohmic heating.}}
\label{fig:kink_str8_ke-4}%
\end{figure*}

@@

@@

\begin{figure*}
  \centering
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{kinetic_energy-3.pdf}
      \caption{Kinetic Energy}
      \label{fig:kink_ke-3}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{kinetic_energy_log-3.pdf}
      \caption{Growth rate estimation}
      \label{fig:kink_ke_log-3}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{heating_r-3.pdf}
      \caption{Cumulative heat}
      \label{fig:heating_r-3}
    \end{subfigure}
\mycaption{Kinetic energy \rev{and heating} as a function of time in the cases where
$\eta=10^{-3}$.}{The results from both viscosity models are shown. The flute
instability appears earlier than where $\eta=10^{-4}$ and the growth rate of
the kink instability is decreased. \rev{The cumulative heating $\langle Q_{*} \rangle$ where $*$ is either $\nu$ for viscous heating or $\eta$ for Ohmic heating is the total heat integrated over both time and space up to a time $t$. While the heat generated via viscous heating is orders of magnitude lower when using anisotropic viscosity, Ohmic heating is enhanced by the use of the anisotropic model.}}
\label{fig:kink_str8_ke-3}%
\end{figure*}
